gratia: An R package for exploring generalized additive models

### 2024-11-21 paper.Rmd
add comment regarding what the proj4 string is in the code as per #304

*gratia* can handle distributional GAMs fitted with *mgcv* and also *GJRM*'s `gamlss()`. Below, the estimated smooths from `m2` are plotted using `draw()`
```{r m2-draw, fig.show = "hide", dependson = "fit-chl-lsslmodel", cache = TRUE, fig.pos = "t!", out.width = ".8\\linewidth"}
crs <- "+proj=ortho +lat_0=20 +lon_0=-40"
draw(m2, crs = crs, default_crs = 4326, dist = 0.05, rug = FALSE)
```
Here, we see a specialised plot drawn for spline-on-the-sphere smooths $f(\mathtt{lat}_i,\mathtt{lon}_i)$ (Figure \ref{fig:m2-draw}), which uses `ggplot2::coord_sf()` and functionality from the *sf* package [@Pebesma2018-ws; @Pebesma2023-fe] to visualise the smooth via an orthographic projection.

>>>>

*gratia* can handle distributional GAMs fitted with *mgcv* and also *GJRM*'s `gamlss()`. Below, the estimated smooths from `m2` are plotted using `draw()`
```{r m2-draw, fig.show = "hide", dependson = "fit-chl-lsslmodel", cache = TRUE, fig.pos = "t!", out.width = ".8\\linewidth"}
# Define the coordinate system to use for plotting on a map
crs <- "+proj=ortho +lat_0=20 +lon_0=-40"
draw(m2, crs = crs, default_crs = 4326, dist = 0.05, rug = FALSE)
```
Here, we see a specialised plot drawn for spline-on-the-sphere smooths $f(\mathtt{lat}_i,\mathtt{lon}_i)$ (Figure \ref{fig:m2-draw}), which uses `ggplot2::coord_sf()` and functionality from the *sf* package [@Pebesma2018-ws; @Pebesma2023-fe] to visualise the smooth via an orthographic projection.
